### 2023-03-17 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

Electrohydrodynamic Atomization (EHDA), also known as Electrospray (ES), is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.
The electric current flowing transported by the spray reveals characteristic shapes for different spray modes.
Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
Industrial applications demand automated stabilization of a spray mode. 
This can be achieved by a closed-loop control system. 
This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode. 
In the figure we can see how EHDA experiment works.

@@

As pesquisas de EHDA têm contribuído como uma importante ferramenta para
o desenvolvimento da tecnologia da água (dessalinização térmica e recuperação de metais), ciências dos materiais (nanofibras e
fabricação de nanoesferas, recuperação de metal, membranas seletivas e baterias) e aplicação biomédica
(encapsulamento). Além disso, o projeto está integrado à estratégia de Transição Energética e à Agenda de Inovação
Agricultura, água e alimentos, tecnologias facilitadoras essenciais (KETs). Embora existam aplicações de EHDA em
indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.
A corrente elétrica que flui transportada pelo spray revela formas características para diferentes modos de atomização.
Essas formas não podem ser simplesmente resumidas por seu valor médio. Na figura um podemos ver um exemplo de cone-jet
modo eletrospray.

>>>>

Electrohydrodynamic Atomization (EHDA) is a way to disintegrate a liquid into droplets by exposing it to a strong electric field.\cite{prunet}
The balance beetween capilary forces and the eletric field on the charged liquid defines the spraying dynamics and droplet size.
The electric current transported by the spray reveals characteristic shapes for different spray modes.
Signal processing techniques can allow a non-visual classification of the spray mode based on the electric current shape.\cite{Sjaaks}
The spray process imposes noise and random sequences on the measured signal making its classification not a trivial task. 
Industrial applications demand automated stabilization of a spray mode. 
This can be achieved by a closed-loop control system. 
This project is about to develop an application that can classify what dynamics the EHDA experiment is current in and control the variables to stabilize in the desired mode.

@@

As pesquisas de EHDA têm contribuído como uma importante ferramenta para
o desenvolvimento da tecnologia . Embora existam aplicações de EHDA em
indústria, a estabilização do modo de pulverização de jato cônico é feita empiricamente e com base em medições de corrente média.
A corrente elétrica que flui transportada pelo spray revela formas características para diferentes modos de atomização.
Essas formas não podem ser simplesmente resumidas por seu valor médio. Na figura um podemos ver um exemplo de cone-jet
modo eletrospray.

### 2023-03-17 Documentation/WT group/NHL/systemDescription/systemDescription.tex
documentation

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/drippingexample.png}
      \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/conejetexample.png}
      \caption{Cone Jet}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/multijetexample.png}
      \caption{Multi Jet}
  \end{figure}

@@

@@

@@

>>>>

The electrospraying of liquids herein is referred to as electrohydrodynamic atomization (EHDA). The atomization by primarily electrical (electro) forces of a liquid (hydro) that is moving (dynamic) during the atomization captures the essence of the phenomena.\cite{Grace}
That motion applies to the liquid certain velocity that is not enough to create the spray alone. Therefore, the eletric field itself is the responsible for the spraying dynamics.\cite{prunet}

The stable balance between the capilary and field forces on the liquid suggest a \emph{quasi static} dynamics.
For this reason with a controlled enviroment we can reach a certain stable spraying mode as can be seen in the Figure \ref{fig:ehda_setup_ex2}.

\begin{figure}[H]
  \centering
  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
  \caption{EHDA physical concept \cite{Gabriel}}
  \label{fig:ehda_setup_ex2}
\end{figure}

\section{Spraying modes}
\label{sec:spraying_modes_subsec}

Since 1915 with his pioneering work in EHDA, Zeleny observed several functioning modes with very different characteristics.
Years later the same phenomena was noticed by other scientists but the classification of these modes were still not well defined by the community.
For that Cloupeau and Prunet-Foch proposed spray mode classifications based in what they have seen experimentally and it's still being used as basis for EHDA researchs.\cite{prunet}

The Figures \ref{fig:dripping_camera_example}, \ref{fig:cone_camera_jet_example}, \ref{fig:multi_camera_jet_example} shows the 3 spraying dynamics that we are most intersted in this project.

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/drippingexample.png}
      \label{fig:dripping_camera_example}
      \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/conejetexample.png}
      \label{fig:cone_camera_jet_example}
      \caption{Cone Jet}
  \end{figure}

  \begin{figure}[H]
      \center
      \includegraphics[width=3cm]{Figuras/multijetexample.png}
      \label{fig:multi_camera_jet_example}
      \caption{Multi Jet}
  \end{figure}

@@

Through the various classifications defined we are going to work aggregating some of them and separating beetween 5 modes as shown above:

\subsection{Dripping}
\label{subsec:dripping}

In Dripping mode the eletric field applied is not enough to change the meniscus shape, phenomena called field enhanced dripping.
In that situation the liquid droplet has, in general, size bigger than the capilary and low frequency intervals between each drop.

\subsection{Intermittent}
\label{subsec:Intermittent}

Intermittent mode is defined when the eletric field forces starts to have a considerable effect in the meniscus and droplet formation. 
In this mode the droplet size is smaller than the nozzle, phenomena called microdripping, and the dripping frequency increases with the increasing of the field applied.

\subsection{Cone Jet}
\label{subsec:Cone Jet}

\subsection{Multi Jet}
\label{subsec:Multi Jet}

\subsection{Corona sparks}
\label{subsec:Corona sparks}

@@

\subsection{Setup Organization}
\label{subsec:setup_organization}

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
  \caption{EHDA experiment setup \cite{Luewton}}
  \label{fig:ehda_setup}
\end{figure}

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/setup_pic.jpg}}
  \caption{EHDA automation system setup}
  \label{fig:setup_pic}
\end{figure}

\subsection{Instruments Used}
\label{subsec:instruments}

@@

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
  \caption{EHDA automation system setup}
  \label{fig:microdripping_current_pic}
\end{figure}
